Impact ionization processes in a photodriven Mott insulator: influence of phononic dissipation

### 2022-08-24 Paper1.tex
changes Enrico 24.08.2022

We study a model for photovoltaic energy collection consisting of a Mott insulating layer in presence of acoustic phonons, coupled to two wide-band fermion leads at different chemical potentials and driven by a periodic electric field. We treat electron correlations with nonequilibrium dynamical mean-field theory (DMFT) using the so-called auxiliary master equation approach as impurity solver and include dissipation by acoustic phonons via the Migdal approximation. For a small hybridization to the leads, we obtain a peak in the photocurrent as a function of the driving frequency which can be associated with impact ionization processes.
For larger hybridizations the shallow peak suggests a suppression of impact ionization with respect to direct photovoltaic excitations. Acoustic phonons slightly enhance the photocurrent for small driving frequencies and suppress it at frequencies around the main peak. This effect occurs at all considered hybridization strengths.

@@

For this goal we consider the simplified model shown in Fig.~\ref{fig:setup}, consisting of a Hubbard layer located between two leads. The metallic leads have themselves a wide band, which is effectively narrowed due to the weak coupling to intermediate layers which we take as models for the contacts. Electrons on the Hubbard layer interact locally with acoustic phonons. An external periodic electric field induces a Floquet steady state with a current flowing from the lead with the lower to the higher chemical potential, thus transferring its energy.
 We address this periodic problem
 via nonequilibrium Floquet dynamical mean-field theory (F-DMFT).

@@

Our goal is to investigate the occurrence of II in this photovoltaic setup and how it is affected by the presence of phonons. 
Specifically we study the behavior of the photovoltaic current, the spectral properties as well as the double occupation as a function of the hybridization strength and the properties of the phonons. Our analysis can only provide qualitative results, while quantitative comparisons with experimental systems require a more realistic setup and are beyond the scope of this work.

We find that a small hybridization to the leads is more favorable for II than a larger one. II therefore plays a crucial role in compensating the smaller charge injection, giving the same order of magnitude in the photocurrent as for the larger hybridization.
In all cases, the interaction with phonons slightly enhances the photocurrent for small driving frequencies, while suppressing it in vicinity of the main peak.

@@

The local e-ph coupling is included as in Ref.~\cite{ma.ga.22u} with an acoustic phonon branch attached to each lattice site via the Hamiltonian 
\begin{equation}\label{eq:e-ph_ham} 
\hat{H}_{\text{e-ph}} = g \sum_{i\sigma} \hat{n}_{i\sigma} \hat{x}_{i},  
\end{equation}
with $g$ as e-ph coupling and $\hat{x}_{i} \equiv \frac{1}{\sqrt{2}} \left( \hat{b}^{\dagger}_{i} + \hat{b}_i \right)$, where $\hat{b}^{\dagger}_{i}$ ($\hat{b}_{i}$) creates (annihilates) a phonon of the acoustic branch at site $i$, with dispersion relation described by $\hat{H}_{\text{ph}}$~\cite{ma.ga.22u}.  Details on the leads are provided in~\ref{sec:Dyson_equation}.

For mathematical simplicity~\cite{ge.ko.92,ao.ts.14}, 
 we consider the correlated central region as a $d$-dimensional layer and consider the limit of infinite dimensions $d \rightarrow \infty$ by rescaling the hopping as $t_{\text{c}}=t^{\ast}/2\sqrt{d}$. Taking $a=1$, sums over the crystal momentum ${\bf k}$ of a generic quantity $\chi$ read $\sum_{{\bf k}} \chi(\omega,{\bf k}) \rightarrow \int d\epsilon \int   d\overline{\epsilon} \ \rho(\epsilon,\overline{\epsilon}) \chi(\omega;\epsilon,\overline{\epsilon})$ with $\rho(\epsilon,\overline{\epsilon}) = (1/\pi t^{\ast 2}) \exp[-( \epsilon^{2} + \overline{\epsilon}^{2})/t^{\ast 2}]$ as the joint density of states~\cite{ts.ok.08} and with
% 
\begin{align}\label{eq:d-dim_crystal_dep}
\begin{split}  
\epsilon & = -2t_{\text{c}} \sum_{i=1}^{d} \cos(k_i a), \\  
\overline{\epsilon}& = -2t_{\text{c}}\sum_{i=1}^{d} \sin(k_i a). \\
\end{split}  
\end{align}
%

Within the remainder of this paper we set $\hbar = k_{\text{B}} = a = 1 = -q$, $t^{\ast}=2\sqrt{2}$ ~\footnote{With such choice for $t^{\ast}$ we reproduce the DOS of a 2D layer with $t_{\text{c}}=1$  in order to compare with Ref.~\cite{so.do.18}.} and $t_r \equiv \frac{t^{\ast}}{2\sqrt{2}}=1$ as unit of energy.

@@

To correctly describe the nonequilibrium periodic steady state, we use the Floquet generalization of the nonequilibrium Green's function (NEGF) approach~\cite{ts.ok.08}. Every function $G(t,t^{\prime})$ satisfying the periodicity relation $G(t,t^{\prime})=G(t+\tau,t^{\prime}+\tau)$, with $\tau=2\pi/\Omega$ as the period related to the external driving frequency $\Omega$, may be represented as~\cite{ts.ok.08,sc.mo.02u,jo.fr.08}

@@

The lattice Floquet GF of our setup obeys the Dyson equation

\begin{equation}\label{eq:FullDysonEq}
\underline{{\bf G}}^{-1}(\omega_n;\epsilon,\overline{\epsilon}) = \underline{{\bf G}}^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}_{\text{e-ph}}(\omega_n;\epsilon,\overline{\epsilon}).
\end{equation}

@@

The electron self-energy (SE) $\underline{\bf{\Sigma}}$ is obtained from F-DMFT and therefore independent of the crystal momentum, i.e. $\underline{\bf{\Sigma}}(\omega;\epsilon,\overline{\epsilon}) \simeq \underline{\bf{\Sigma}}(\omega)$. Further details are given in Sec.~\ref{sec:FDMFT_implementation}.

The e-ph SE is also included locally as $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega;\epsilon,\overline{\epsilon}) \simeq \underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$. In terms of the Keldysh contour time arguments $z$ and $z^\prime$, it has the form

@@

The Keldysh components of the non-interacting phonon GF $\kel{D}_{\text{ph}}(t,t^{\prime})$ are given by~\cite{ao.ts.14}
%
\begin{align}\label{eq:Ph_Prop_time}
\begin{split} 
D^{\text{R}}_{\text{ph}}(t,t^{\prime}) & = -\ii \theta(t-t^{\prime}) \int \dd\omega \ \ee^{-\ii\omega\left(t-t^{\prime}\right)} A_{\text{ph}}(\omega), \\
D^{>}_{\text{ph}}(t,t^{\prime}) & = -\ii \int \dd\omega \ \ee^{-\ii\omega\left(t-t^{\prime}\right)} A_{\text{ph}}(\omega) \left[ 1 + b(\omega) \right] \\
D^{<}_{\text{ph}}(t,t^{\prime}) & = -\ii \int \dd\omega \ \ee^{-\ii\omega\left(t-t^{\prime}\right)} A_{\text{ph}}(\omega) \ b(\omega), \\
\end{split}, 
\end{align}
%
where $b(\omega)=1/(\ee^{\beta\omega}-1)$ is the Bose-Einstein distribution function at inverse temperature $\beta$. We focus on acoustic phonons, with spectral function $A_{\text{ph}}(\omega) = (\omega/\omega^{2}_{\text{ph}}) \ee^{-| \omega|/\omega_{\text{ph}}}$,  $\omega_{\text{ph}}$ being a soft cutoff frequency~\cite{pi.li.21}. The retarded and Keldysh components of the e-ph SE are easily extracted from  Eq.~\eqref{eq:backbone_e-ph_SE} and can be found in Ref.~\cite{ma.ga.22u}.

@@

We briefly describe now the self-consistent F-DMFT scheme used.
(i) We start from an initial guess for the electron SE $\kel{\mat{\Sigma}}(\omega)$ and set $\kel{\mat \Sigma}_{\text{e-ph}}(\omega)=0$. (ii) Then we compute the local electron GF as 
%  
\begin{equation}\label{eq:Lat_LocGF}
\begin{split}
\kel{\mat G}_{\text{loc}}(\omega) &= \int \dd\epsilon \int \dd\overline{\epsilon} \ \rho(\epsilon,\overline{\epsilon}) \times \\ 
&\times \left[\kel{\mat G}^{-1}_{0}(\omega,\epsilon,\overline{\epsilon}) - \kel{\mat\Sigma}(\omega) - \kel{\mat \Sigma}_{\text{e-ph}}(\omega) \right]^{-1}.
\end{split}
\end{equation}
% 
(iii) Using Eq.~\eqref{eq:backbone_e-ph_SE}, we obtain the phonon contribution to the SE $\kel{\mat{\Sigma}}_{\text{e-ph}}(\omega)$.
(iv) The problem is mapped onto a single impurity plus bath, whose hybridization function
is given by
%
\begin{equation}\label{eq:imp_Dyson_eq}
\kel{\mat{\Delta}}(\omega) = \kel{\mat{g}}^{-1}_{0,\text{site}}(\omega) - \kel{\mat{G}}^{-1}_{\text{loc}}(\omega) - \kel{\mat{\Sigma}}(\omega),
\end{equation}   
%  
where $\kel{\mat{g}}^{-1}_{0,\text{site}}(\omega)$ is defined as in Eq.~\eqref{eq:inv_non-int_lat_GF_comps} with $\varepsilon_{mn}(\epsilon,\overline{\epsilon})=0$. (v) The nonequilibrium many-body impurity problem is solved according to the procedure in Sec.~\ref{sec:amea}, leading to the new
 $\kel{\mat{\Sigma}}(\omega)$. (vi) We insert the electron and e-ph SEs into step (ii) and iterate the steps (ii)-(vi) until convergence.

\subsubsection{Floquet-diagonal self-energy approximation}
\label{sec:FDSA}

From Eq.~\eqref{eq:imp_Dyson_eq}, we obtain the bath hybridization function $\kel{\mat\Delta}(\omega)$ whose periodic time-dependence is encoded in its Floquet structure. Being interested in photovoltaic effects, we follow Ref.~\cite{so.do.18} and use the Floquet-diagonal self-energy approximation (FDSA) for which Floquet off-diagonal terms in the electron SE $\kel{\mat{\Sigma}}(\omega)$ are neglected. In addition, we employ FDSA also for the phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ \footnote{In the parameters range in which FDSA is justified for the electron SE $\kel{\mat{\Sigma}}(\omega)$ (Sec.~\ref{sec:results}), the diagonal terms of the phonon SE $\underline{\Sigma}_{mm,\text{e-ph}}(\omega)$ are orders of magnitude bigger than the off-diagonal ones}. Consequently, we only consider the 
 $(0,0)$-Floquet matrix element of Eq.~\eqref{eq:imp_Dyson_eq} in the impurity problem, which therefore becomes stationary. It is sufficient to restrict oneself to the $(0,0)$ component, since the other diagonal components can be reconstructed by using the property $\kel{\Sigma}_{mm}(\omega) = \kel{\Sigma}_{00}(\omega+m\Omega)$.

\subsubsection{Auxiliary master equation approach}
\label{sec:amea}

In the following, we briefly summarize the impurity solver used in step (v) of the DMFT self-consistent loop described in Sec.~\ref{sec:FDMFT_implementation}. In order to solve the many-body problem,
 we use the auxiliary master equation approach (AMEA)~\cite{ar.kn.13,do.nu.14,do.ga.15,do.so.17}. Therein, we map the impurity problem onto an auxiliary open quantum system (AOQS) consisting of a finite number of bath sites $N_{\text{B}}$ attached to Markovian reservoirs described by the Lindblad equation. The  hybridization function $\kel{\Delta}_{\text{aux}}(\omega)$ of this AOQS is obtained by fitting the original DMFT one. The key point is that the many-body problem of this AOQS can be solved exactly 
using standard many-body-diagonalization methods, as long as  $N_{\text{B}}$ is small.
The accuracy of this solution is set by the difference between
 $\kel{\Delta}_{\text{aux}}$ and $\kel{\Delta}$, which  becomes exponentially  small with increasing $N_{\text{B}}$.

@@

The photocurrent flowing from the left fermion lead to the right one, passing through the correlated layer is given by 
% 
\begin{align}
j_{\text{l}\rightarrow\text{r}}&=v^2\int_{-\Omega/2}^{\Omega/2}\frac{\dd\omega}{2\pi} \int \dd\epsilon \int \dd\overline{\epsilon} \rho(\epsilon,\overline{\epsilon}) \rre\Tr(\boldsymbol{J})\label{eq: Current furmula_Omega}\\
&= v^2\int_{-\infty}^{+\infty}\frac{\dd\omega}{2\pi} \int \dd\epsilon \int \dd\overline{\epsilon} \rho(\epsilon,\overline{\epsilon}) \rre(J_{00}),\label{eq: Current furmula_00}
\end{align}
% 
where
% 
\begin{equation}
  \boldsymbol{J}=\left[\boldsymbol{G}^{\text{R}}(\boldsymbol{g}_{\text{b},\text{l}}^{\text{K}}-\boldsymbol{g}_{\text{b},\text{r}}^{\text{K}})+\boldsymbol{G}^{\text{K}}(\boldsymbol{g}_{\text{b},\text{l}}^{\text{A}}-\boldsymbol{g}_{\text{b},\text{r}}^{\text{A}})\right]
\end{equation}
% 
is taken from Ref.~\cite{so.do.18}. Of the two equivalent expressions, Eq.~\eqref{eq: Current furmula_00} is used in practice.

The local electronic spectral function (DOS) reads
%  
\begin{equation}
\label{eq:el_spectral_function}
 A(\omega)=-\frac{1}{\pi}\iim[G_{\text{loc},00}^{\text{R}}(\omega)],
\end{equation}
% 
where $G^{\text{R}}_{\text{loc},00}$ is the time-averaged retarded component of the GF given in Eq.~\eqref{eq:Lat_LocGF}.
Combining it with the time-averaged Keldysh component gives the occupation function
\begin{equation}
N(\omega) = \frac{1}{4\pi} [\iim(G^{\text{K}}_{\text{loc},00})-2\iim(G^{\text{R}}_{\text{loc},00})].
\end{equation}

@@

In order to study II in a Mott insulating layer, we set the bands to achieve the energy scheme shown in Fig.~\ref{fig:energy_setup}(a).

 We follow Ref.~\cite{so.do.18} and choose $U=12$ and $E_0=2$. The fermion leads and acoustic phonons have temperature $T=0.02$. We consider a particle-hole symmetric system with $\Gamma_{\text{l}}=\Gamma_{\text{r}}=0.37$, $t_{\text{l}}=t_{\text{r}}=1.7$, $\varepsilon_{\text{l}/\text{r}}=\mp 6$ and $v_{\text{l}}=v_{\text{r}}=v$. The parameters $t_{\text{l/r}}$, $\varepsilon_{\text{l/r}}$, and  $\Gamma_{\text{l/r}}$ are chosen such that the leads' DOS approximately coincides with the Hubbard bands, i.e. they exhibit a \textquoteleft bandwidth\textquoteright~\footnote{Notice that the support of its spectrum is formally infinite. $W_{\text{b}}$ is the value at which the spectrum gets  suppressed.} $W_{\text{b}}\approx 8$ and are centered at the same position. The chemical potentials are set to $\mu_{\text{l}/\text{r}} =\mp 1$, so that a current from left to right is produced by energy taken from the driving.

Due to the hybridization with the leads, the local DOS of the Hubbard layer only features a pseudogap
 $\Delta_{\text{pg}} \approx 4$.
All simulations are carried out with the dimensionless factor $\alpha\equiv t_{r}E_0/\Omega^{2}<0.5$ for which the FDSA is justified~\footnote{In Ref.~\cite{so.do.18} the factor is defined as $\alpha=t_{c}E_0/\Omega^{2}$ and $t_{\text{c}}=1$. Setting $t_{r}=1$, we define for consistency $\alpha$ as in the main text.} and first-order photon absorption processes are dominant. Whenever the electron-phonon interaction is switched on, we take $g=0.8$ and unless stated otherwise $\omega_{\text{ph}}=0.1$.

@@

\includegraphics[width=0.85\linewidth]{./figures_Paper1/energy_setup.pdf}
\caption{(Color online) Schematic representation of the processes occuring in the model considered. Red bands on the left and right describe the leads' DOS, where the dark color highlights occupied states and the light color empty states. Green bands are the LHB and UHB of the central layer. The vertical axis represents the energy. Panel (a) sketches the quantities introduced at the beginning of Sec.~\ref{sec:results}. Panel (b) illustrates a direct excitation process, in which an electron is excited by a photon with energy $\Omega$ (yellow arrow) to the UHB and escapes into the right lead (red arrow). Panel (c) displays an II process, where the photoexcited electron in the UHB excites a second electron from LHB to UHB (black arrows) and both escape into the right lead. In the nonequilibrium steady state considered here, only processes recovering the initial configuration are allowed.} 
\label{fig:energy_setup}
\end{figure}

\subsection{Energy considerations and physical processes}
\label{sec:explicative_scheme}

>>>>

We study a model for photovoltaic energy collection consisting of a Mott insulating layer in presence of acoustic phonons, coupled to two wide-band fermion leads at different chemical potentials and driven by a periodic electric field. We treat electron correlations with nonequilibrium dynamical mean-field theory (DMFT) using the so-called auxiliary master equation approach as impurity solver and include dissipation by acoustic phonons via the Migdal approximation. For a small hybridization to the leads, we obtain a peak in the photocurrent as a function of the driving frequency which can be associated with impact ionization processes.
For larger hybridizations the shallow peak suggests a suppression of impact ionization with respect to direct photovoltaic excitations. Acoustic phonons slightly enhance the photocurrent for small driving frequencies and suppress it at frequencies around the main peak 
% This effect occurs at all considered hybridization strengths.
 at all considered hybridization strengths.

@@

For this goal we consider the simplified model shown in Fig.~\ref{fig:setup}, consisting of a Hubbard layer located between two leads. The leads have themselves a wide band, as expected for good condutors, which are effectively narrowed due to the weak coupling to intermediate layers which we take as simplified models for the contacts. Electrons on the Hubbard layer interact locally with acoustic phonons. An external periodic electric field induces a Floquet steady state with a current flowing from the lead with the lower to the higher chemical potential, thus transferring its energy.
 We address this periodic problem
 via nonequilibrium Floquet dynamical mean-field theory (F-DMFT).

@@

Our goal is to investigate the occurrence of II in this photovoltaic setup and how it is affected by the presence of phonons. 
Specifically we study the behavior of the photovoltaic current, the spectral properties as well as the double occupation as a function of the hybridization strength and the properties of the phonons. Our analysis can only provide qualitative results, while quantitative comparisons with experimental systems require a more realistic setup and are beyond the scope of this work.
Our calculations show that a small hybridization to the leads is more favorable for II than a larger one. II therefore plays a crucial role in compensating the smaller charge injection, giving the same order of magnitude in the photocurrent as for the larger hybridization.
In all cases, the interaction with phonons slightly enhances the photocurrent for small driving frequencies, while suppressing it in vicinity of the main peak.

@@

Phonons are 
%The local e-ph coupling is
 included as in 
%EACOMM check, put also previous references
Ref.~\cite{ma.ga.22u} in the form of  acoustic  branches attached to each lattice site and coupled to the electrons via the Hamiltonian 
\begin{equation}\label{eq:e-ph_ham} 
\hat{H}_{\text{e-ph}} = g \sum_{i\sigma} \hat{n}_{i\sigma} \hat{x}_{i},  
\end{equation}
with $g$ as e-ph coupling and $\hat{x}_{i} \equiv \frac{1}{\sqrt{2}} \left( \hat{b}^{\dagger}_{i} + \hat{b}_i \right)$, where $\hat{b}^{\dagger}_{i}$ ($\hat{b}_{i}$) creates (annihilates) a phonon of the acoustic branch at site $i$, with dispersion relation described by $\hat{H}_{\text{ph}}$~\cite{ma.ga.22u}, see below.  
In contrast to Holstein phonons these have a finite bandwidth which is more effective in energy dissipation.
Details on the leads are provided in~\ref{sec:Dyson_equation}.

For mathematical simplicity~\cite{ge.ko.92,ao.ts.14}, 
 we consider the correlated central region as a $d$-dimensional layer and consider the limit of infinite dimensions $d \rightarrow \infty$ by rescaling the hopping as 
%EACOMM check parenthesis
$t_{\text{c}}=t^{\ast}/(2\sqrt{d})$. Taking $a=1$, sums over the crystal momentum ${\bf k}$ of a generic quantity $\chi$ read $\sum_{{\bf k}} \chi(\omega,{\bf k}) \rightarrow \int d\epsilon \int   d\overline{\epsilon} \ \rho(\epsilon,\overline{\epsilon}) \chi(\omega;\epsilon,\overline{\epsilon})$ with $\rho(\epsilon,\overline{\epsilon}) = (1/\pi t^{\ast 2}) \exp[-( \epsilon^{2} + \overline{\epsilon}^{2})/t^{\ast 2}]$ as the joint density of states~\cite{ts.ok.08} and with
% 
\begin{align}\label{eq:d-dim_crystal_dep}
\begin{split}  
\epsilon & = -2t_{\text{c}} \sum_{i=1}^{d} \cos(k_i a), \\  
\overline{\epsilon}& = -2t_{\text{c}}\sum_{i=1}^{d} \sin(k_i a). \\
\end{split}  
\end{align}
%

Within the remainder of this paper we choose our units so that  $\hbar = k_{\text{B}} = a = 1 = -q$, $t^{\ast}=2\sqrt{2}$ ~\footnote{With such choice for $t^{\ast}$ we reproduce the DOS of a 2D layer with $t_{\text{c}}=1$  in order to compare with Ref.~\cite{so.do.18}.}, and $t_r \equiv \frac{t^{\ast}}{2\sqrt{2}}=1$ as unit of energy.

@@

To correctly describe the nonequilibrium periodic steady state, we use the Floquet generalization of the nonequilibrium Green's function (NEGF) 
approach~\cite{ts.ok.08,sc.mo.02u,jo.fr.08}. Every function $G(t,t^{\prime})$ satisfying the periodicity relation $G(t,t^{\prime})=G(t+\tau,t^{\prime}+\tau)$, with $\tau=2\pi/\Omega$ as the period related to the external driving frequency $\Omega$, may be represented as~\cite{ts.ok.08,sc.mo.02u,jo.fr.08}

@@

The lattice Floquet GF of our setup obeys the Dyson equation 
\begin{equation}\label{eq:FullDysonEq}
\underline{{\bf G}}^{-1}(\omega_n;\epsilon,\overline{\epsilon}) = \underline{{\bf G}}^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}_{\text{e-ph}}(\omega_n;\epsilon,\overline{\epsilon}) \;,
\end{equation}
where in our approximation the electron-electron $ \underline{{\bf \Sigma}}(\omega_n;\epsilon,\overline{\epsilon})$ and electron-phonon $\underline{{\bf \Sigma}}_{\text{e-ph}}(\omega_n;\epsilon,\overline{\epsilon})$ self energies contribute independently to the total self energy~\footnote{In fact there is an indirect feedback via the DMFT self-consistency.}

@@

The electron self-energy (SE) $\underline{\bf{\Sigma}}$ is obtained from F-DMFT and therefore, in this approximation, independent of the crystal momentum, i.e. $\underline{\bf{\Sigma}}(\omega;\epsilon,\overline{\epsilon}) \simeq \underline{\bf{\Sigma}}(\omega)$. Further details are given in Sec.~\ref{sec:FDMFT_implementation}. 
In the same spirit, the e-ph SE is included locally as $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega;\epsilon,\overline{\epsilon}) \simeq \underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$. In terms of the Keldysh contour time arguments $z$ and $z^\prime$, it has the form

@@

The Keldysh components of the non-interacting phonon GF $\kel{D}_{\text{ph}}(t,t^{\prime})$ are given by~\cite{ao.ts.14}
%
\begin{align}\label{eq:Ph_Prop_time}
\begin{split} 
D^{\text{R}}_{\text{ph}}(t,t^{\prime}) & = -\ii \theta(t-t^{\prime}) \int \dd\omega \ \ee^{-\ii\omega\left(t-t^{\prime}\right)} A_{\text{ph}}(\omega), \\
D^{>}_{\text{ph}}(t,t^{\prime}) & = -\ii \int \dd\omega \ \ee^{-\ii\omega\left(t-t^{\prime}\right)} A_{\text{ph}}(\omega) \left[ 1 + b(\omega) \right] \\
D^{<}_{\text{ph}}(t,t^{\prime}) & = -\ii \int \dd\omega \ \ee^{-\ii\omega\left(t-t^{\prime}\right)} A_{\text{ph}}(\omega) \ b(\omega), \\
\end{split}, 
\end{align}
%
where $b(\omega)=1/(\ee^{\beta\omega}-1)$ is the Bose-Einstein distribution function at inverse temperature $\beta$. We consider acoustic phonons, with spectral function $A_{\text{ph}}(\omega) = (\omega/\omega^{2}_{\text{ph}}) \ee^{-| \omega|/\omega_{\text{ph}}}$,  $\omega_{\text{ph}}$ being a soft cutoff frequency~\cite{pi.li.21}. The retarded and Keldysh components of the e-ph SE are easily extracted from  Eq.~\eqref{eq:backbone_e-ph_SE} and can be found in Ref.~\cite{ma.ga.22u}.

@@

For completeness, we now
 briefly describe now the self-consistent F-DMFT scheme used.
(i) We start from an initial guess for the electron SE $\kel{\mat{\Sigma}}(\omega)$ and set $\kel{\mat \Sigma}_{\text{e-ph}}(\omega)=0$. (ii) Then we compute the local electron GF as 
%  
\begin{equation}\label{eq:Lat_LocGF}
\begin{split}
\kel{\mat G}_{\text{loc}}(\omega) &= \int \dd\epsilon \int \dd\overline{\epsilon} \ \rho(\epsilon,\overline{\epsilon}) \times \\ 
&\times \left[\kel{\mat G}^{-1}_{0}(\omega,\epsilon,\overline{\epsilon}) - \kel{\mat\Sigma}(\omega) - \kel{\mat \Sigma}_{\text{e-ph}}(\omega) \right]^{-1}.
\end{split}
\end{equation}
% 
(iii) Using Eq.~\eqref{eq:backbone_e-ph_SE}, we obtain the phonon contribution to the SE $\kel{\mat{\Sigma}}_{\text{e-ph}}(\omega)$.
(iv) The problem is mapped onto a single impurity plus bath, whose hybridization function
is given by
%
\begin{equation}\label{eq:imp_Dyson_eq}
\kel{\mat{\Delta}}(\omega) = \kel{\mat{g}}^{-1}_{0,\text{site}}(\omega) - \kel{\mat{G}}^{-1}_{\text{loc}}(\omega) - \kel{\mat{\Sigma}}(\omega),
\end{equation}   
%  
where $\kel{\mat{g}}^{-1}_{0,\text{site}}(\omega)$ is defined as in Eq.~\eqref{eq:inv_non-int_lat_GF_comps} with $\varepsilon_{mn}(\epsilon,\overline{\epsilon})=0$. (v) The nonequilibrium many-body impurity problem is solved according to the procedure in Sec.~\ref{sec:amea}, leading to the new
 $\kel{\mat{\Sigma}}(\omega)$. (vi) We insert the electron and e-ph SEs into step (ii) and iterate the steps (ii)-(vi) until convergence.

%EACOMM I eliminated this and the next subsubsection, is this okay?  
%\subsubsection{Floquet-diagonal self-energy approximation}
%\label{sec:FDSA}

%EACOMM check this paragraph, which I changed a bit
Eq.~\eqref{eq:imp_Dyson_eq} gives the bath hybridization function $\kel{\mat\Delta}(\omega)$ whose periodic time-dependence is encoded in its Floquet structure. 
This means that, in principle, one would have to solve a time-periodic impurity problem leading to a non-diagonal self-energy in general. However, in 
 Ref.~\cite{so.do.18} it was argued that for the electric field strengths considered, non-diagonal terms in the Floquet SE $\kel{\mat{\Sigma}}(\omega)$  can be safely neglected with respect to the diagonal ones. We follow this argument and adopt here 
this Floquet-diagonal self-energy approximation (FDSA) as well.
 In addition, it turns out that also for the 
 phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ this approximation is justified\footnote{More specifically, we have verified that in the parameters range in which FDSA is justified for the electron SE $\kel{\mat{\Sigma}}(\omega)$ (Sec.~\ref{sec:results}), the off-diagonal terms of the phonon SE $\underline{\Sigma}_{mm,\text{e-ph}}(\omega)$ are orders of magnitude smaller than the diagonal ones}. 
Consequently, we  have to solve a nonequilibrium stationary impurity problem, by using only the  $(0,0)$-Floquet matrix elements of $\kel{\mat{\Sigma}}(\omega)$ and $\kel{\mat\Delta}(\omega)$, 
%Eq.~\eqref{eq:imp_Dyson_eq}, 
as the other diagonal components can be reconstructed by using the property $\kel{\Sigma}_{mm}(\omega) = \kel{\Sigma}_{00}(\omega+m\Omega)$.

%\subsubsection{Auxiliary master equation approach}
%\label{sec:amea}

%We now
% briefly summarize the impurity solver used in step (v) of the DMFT self-consistent loop %described in Sec.~\ref{sec:FDMFT_implementation}. 
In order to solve the electron-electron many-body problem (step (v) of the DMFT self-consistent loop),
 we use the auxiliary master equation approach (AMEA)~\cite{ar.kn.13,do.nu.14,do.ga.15,do.so.17}, which we now briefly summarize. 
Therein, we map the impurity problem onto an auxiliary open quantum system (AOQS) consisting of a finite number of bath sites $N_{\text{B}}$ attached to Markovian reservoirs described by the Lindblad equation. The  hybridization function $\kel{\Delta}_{\text{aux}}(\omega)$ of this AOQS is obtained by fitting the original DMFT one. The key point is that the many-body problem of this AOQS can be solved exactly 
using standard many-body-diagonalization methods, as long as  $N_{\text{B}}$ is small.
The accuracy of this solution is set by the difference between
 $\kel{\Delta}_{\text{aux}}$ and $\kel{\Delta}$, which  becomes exponentially  small with increasing $N_{\text{B}}$.

@@

The photocurrent flowing from the left fermion lead to the right one, passing through the correlated layer is given by two equivalent expressions, adapted from Ref.~\cite{so.do.18}
% 
\begin{align}
j_{\text{l}\rightarrow\text{r}}&=v^2\int_{-\Omega/2}^{\Omega/2}\frac{\dd\omega}{2\pi} \int \dd\epsilon \int \dd\overline{\epsilon} \rho(\epsilon,\overline{\epsilon}) \rre\Tr(\boldsymbol{J})\label{eq: Current furmula_Omega}\\
&= v^2\int_{-\infty}^{+\infty}\frac{\dd\omega}{2\pi} \int \dd\epsilon \int \dd\overline{\epsilon} \rho(\epsilon,\overline{\epsilon}) \rre(J_{00}),\label{eq: Current furmula_00}
\end{align}
% 
where
% 
\begin{equation}
  \boldsymbol{J}=\left[\boldsymbol{G}^{\text{R}}(\boldsymbol{g}_{\text{b},\text{l}}^{\text{K}}-\boldsymbol{g}_{\text{b},\text{r}}^{\text{K}})+\boldsymbol{G}^{\text{K}}(\boldsymbol{g}_{\text{b},\text{l}}^{\text{A}}-\boldsymbol{g}_{\text{b},\text{r}}^{\text{A}})\right].
\end{equation}
% 
In our case, it is convenient to use 
Eq.~\eqref{eq: Current furmula_00}.

The local electronic spectral function (DOS) reads
%  
\begin{equation}
\label{eq:el_spectral_function}
 A(\omega)=-\frac{1}{\pi}\iim[G_{\text{loc},00}^{\text{R}}(\omega)],
\end{equation}
% 
where $G^{\text{R}}_{\text{loc},00}$ is the time-averaged retarded component of the GF given in Eq.~\eqref{eq:Lat_LocGF}.
Combining it with the time-averaged Keldysh component gives the occupation function
\begin{equation}
N(\omega) = \frac{1}{4\pi} [\iim(G^{\text{K}}_{\text{loc},00}(\omega))-2\iim(G^{\text{R}}_{\text{loc},00}(\omega))].
\end{equation}

@@

In order to study II in a Mott insulating layer, we adjust the bands to achieve the energy scheme shown in Fig.~\ref{fig:energy_setup}(a). 
 We follow Ref.~\cite{so.do.18} and take $U=12$ and unless stated otherwise $E_0=2$. The fermion leads and acoustic phonons have temperature $T=0.02$. We consider a particle-hole symmetric system with $\Gamma_{\text{l}}=\Gamma_{\text{r}}=0.37$, $t_{\text{l}}=t_{\text{r}}=1.7$, $\varepsilon_{\text{l}/\text{r}}=\mp 6$ and $v_{\text{l}}=v_{\text{r}}=v$. The parameters $t_{\text{l/r}}$, $\varepsilon_{\text{l/r}}$, and  $\Gamma_{\text{l/r}}$ are chosen such that the leads' DOS approximately overlaps with the Hubbard bands, i.e. they exhibit a \textquoteleft bandwidth\textquoteright~\footnote{Notice that the support of its spectrum is formally infinite. $W_{\text{b}}$ is the value at which the spectrum gets  suppressed.} $W_{\text{b}}\approx 8$ and are centered at the same position. The chemical potentials are set to $\mu_{\text{l}/\text{r}} =\mp 1$, so that a current from left to right is produced by energy taken from the driving.

Due to the hybridization with the leads, the local DOS of the Hubbard layer only features a pseudogap
 $\Delta_{\text{pg}} \approx 4$.
All simulations are carried out with the dimensionless factor $\alpha\equiv t_{r}E_0/\Omega^{2}<0.5$ for which the FDSA is justified~\footnote{In Ref.~\cite{so.do.18} the factor is defined as $\alpha=t_{c}E_0/\Omega^{2}$ and $t_{\text{c}}=1$. Setting $t_{r}=1$, we define for consistency $\alpha$ as in the main text.}.
% and first-order photon absorption processes are dominant.
 Whenever the electron-phonon interaction is included, we take $g=0.8$ and unless stated otherwise $\omega_{\text{ph}}=0.1$.

@@

\includegraphics[width=0.85\linewidth]{./figures_Paper1/energy_setup.pdf}
\caption{(Color online) Schematic representation of the processes occuring in the model considered. Red bands on the left and right describe the leads' DOS, where the dark color highlights occupied states and the light color empty states. Green bands are the LHB and UHB of the central layer. Due to the hybridization with the metallic leads only a pseudogap $\Delta_{\text{pg}}$ is present between the bands. 
 The vertical axis represents the energy. Panel (a) sketches the quantities introduced at the beginning of Sec.~\ref{sec:results}. Panel (b) illustrates a direct excitation process, in which an electron is excited by a photon with energy $\Omega$ (yellow arrow) to the UHB and escapes into the right lead (red arrow). Panel (c) displays an II process, where the photoexcited electron in the UHB excites a second electron from LHB to UHB (black arrows) and both escape into the right lead. In the nonequilibrium steady state considered here, only processes recovering the initial configuration are allowed.} 
\label{fig:energy_setup}
\end{figure}

\subsection{Qualitative Energy considerations and physical processes}
\label{sec:explicative_scheme}
